The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-09-18 paper.tex
Added NT example in Irish
Added a couple of diagrams

\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Ident(SonAngle)}$<$1.5 &$ \mathcal{M}$  \\[0.5ex]
\hline \hline a. & \ding{43} &  C1C2\textipa{@}C3 & 2.0 $\ast$!  & 2.0 $\ast$ &  \\
\hline b.  & & C1\textipa{@}C2C3 & 1.7  & 1.7 $\ast$ & $\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}

@@

\ex. \a. /kork/ $\rightarrow$ [kork], *[kor\textipa{@}k] \\
         {\it Cork} `Cork (place name)' 
     \b. /kork\textipa{@}/ $\rightarrow$ [kork\textipa{@}], *[kor\textipa{@k@}] \\
         {\it corca} `people' 
     \b. /korp/  $\rightarrow$ [korp], *[kor\textipa{@p}] \\
         {\it corp} `body' %TODO : get some NT data in here!
     \z.
     \citep[(39a,b,c)]{carnie.1994}

@@

\ex. No onset clusters in Chaha
     \a. \textipa{k1r@tam} `he lifted up'

@@

\subsubsection{Sonority Angle Analysis}

@@

@@

{\sc Sonority Rise} can explain idiolects \ref{idiolecta} and \ref{idiolectc}, where the cut-off is drawn between rising and level sonority clusters on the one hand and falling sonority clusters on the other, it is less straightforward to explain the behaviour of idiolects \ref{idiolectb} and \ref{idiolectd}. This is because the cluster hierarchy predicted by {\sc Sonority Rise} does not permit a linear separation of [r]-sonorant clusters from the other falling sonority clusters.

>>>>

\vspace{-3em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Ident(SonAngle)}$<$1.5 &$ \mathcal{M}$  \\[0.5ex]
\hline \hline a. & \ding{43} &  C1C2\textipa{@}C3 & 2.0 $\ast$!  & 2.0 $\ast$ &  \\
\hline b.  & & C1\textipa{@}C2C3 & 1.7  & 1.7 $\ast$ & $\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}

@@

\ex. \a. /kork/ $\rightarrow$ [kork], *[kor\textipa{@}k] \\
         {\it Cork} `Cork (place name)' 
     \b. /kork\textipa{@}/ $\rightarrow$ [kork\textipa{@}], *[kor\textipa{@k@}] \\
         {\it corca} `people' 
     \b. /korp/  $\rightarrow$ [korp], *[kor\textipa{@p}] \\
         {\it corp} `body' 
     \b. /\textipa{baNk}/ $\rightarrow$ [\textipa{baNk}], *[\textipa{baN@k}] \\
         {\it banc} `bank'
     \z.
     \citep[(39a,b,c,26c)]{carnie.1994}

@@

\ex. No onset clusters in Chaha
     \a. \textipa{k1r@tam} `he lifted up' \citep[398]{rose.2000}

@@

\subsubsection{Analysis}

@@

\ex. All clusters with a {\sc Sonority Angle} to the left of the dividing line undergo epenthesis while those to the right resist it, with one exception.

\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{point}=[circle,fill=black!25,minimum size=12pt,inner sep=2pt]
  \tikzstyle{line} = [draw, -latex']

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.89254688119*8, 1) {RN};
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {bF};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.5 * 8,2) {};
  \node (dividinglineend)   at (1.5 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.5*8, -0.5) {1.5};
\end{tikzpicture}
}

@@

{\sc Sonority Rise} can explain idiolects \ref{idiolecta} and \ref{idiolectc}, where the cut-off is drawn between rising and level sonority clusters on the one hand and falling sonority clusters on the other, it is less straightforward to explain the behaviour of idiolects \ref{idiolectb} and \ref{idiolectd}. This is because the cluster hierarchy predicted by {\sc Sonority Rise} does not permit a linear separation of [r]-sonorant clusters from the other falling sonority clusters: if RN undergoes epenthesis, we expect that FT and NF should also, but FT never does.

\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{line} = [draw, -latex']
  \node (RT) at (2.5*8, 0)  {RT};
  \node (NT) at (1.67*8,0)  {NT};
  \node (FT) at (1.25*8,0)  {FT};
  \node (TT) at (1*8,-0.5)     {TT};
  \node (RF) at (2*8,0)     {RF};
  \node (NF) at (1.33*8,-0.5)  {NF};
  \node (FF) at (1*8,0)   {FF};
  \node (TF) at (0.8*8,-0.5)   {TF};
  \node (RN) at (1.5*8,0)   {RN};
  \node (NN) at (1*8,0.5)     {NN};
  \node (FN) at (0.75*8,0)  {FN};
  \node (TN) at (0.6*8,0)   {TN};
  \node (RR) at (1*8,1.0)  {RR};
  \node (NR) at (0.67*8,-0.5)  {NR};
  \node (FR) at (0.5*8,0)   {FR};
  \node (TR) at (0.4*8,0)   {TR};
  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
  \node (level) at (1*8,2) {\underline{Level sonority}};
  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,-1.0) {};
  \node (axisend)   at (2.7*8,-1.0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
  \node (0pointlabel) at (0.0,-1.5) {0};
  \node (1pointlabel) at (1.0*8,-1.5) {1};
  \node (2pointlabel) at (2.0*8,-1.5) {2};
  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
\end{tikzpicture}
}
